---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# SpaceX - An R API wrapper for the SpaceX project

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "##",
                      fig.retina = 2,
                      fig.align = "center",
                      fig.path = "README_figs/README-")
```

## Installation

Until now the package is not on CRAN but you can download it via GitHub with the following command:

```{r, eval = FALSE}
if (!require("devtools"))
  install.packages("devtools")
devtools::install_github("JohannesFriedrich/SpaceX")
```


## Introduction

The **R**-package *SpaceX* is an API wrapper for data collected by https://api.spacexdata.com/v2/. You can request available data with different functions:

Function name       | Description                                        | Example
--------------------|----------------------------------------------------| -------
get_SpaceX_info()       | request common information about SpaceX  | get_SpaceX_info()
get_SpaceX_launches()   | request launches                         | get_SpaceX_launches()
get_SpaceX_launchpads() | request launchpad data                   | get_SpaceX_launchpads()
get_SpaceX_capsules()   | request data about capsules              | get_SpaceX_capsules() 
get_SpaceX_rockets()    | request data about different rockets     | get_SpaceX_rockets()  
get_SpaceX_parts()      | request data about parts of capsules or cores  | get_SpaceX_parts(type = "caps")  

## Request basic information from SpaceX API <a id="basic_information"></a>

First we load some needed packages. The function `get_SpaceX_info()` will deliver some information about the company.

```{r, warning=FALSE, message=FALSE}
library(SpaceX)
library(ggplot2)
library(dplyr)

info <- get_SpaceX_info()
```


```{r, eval = FALSE}
info
```

```{r echo=FALSE}
knitr::kable(
  info[,1:7],
  format = "html"
)
```

## Request upcoming starts

```{r upcoming launches}
upcoming <- get_SpaceX_launches("upcoming")
```

```{r, echo = FALSE}
knitr::kable(upcoming[1:3,1:9],
             format = "html")
```

## Play around with data

```{r past_launches}
get_SpaceX_launches() %>% 
ggplot() + 
  geom_bar(aes(launch_year, fill = launch_site$site_name)) +
  facet_grid(rocket$rocket_name~launch_success, scales = "free_x") +
  theme(legend.position = "bottom") + 
  scale_fill_discrete(name = "Launch Site") +
  labs(x = "Year", y = "Counts") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

```

Now we request some data about the used rockets. This can be done with the function `get_SpaceX_rockets()`.

```{r}
rockets <- get_SpaceX_rockets()
```

```{r, echo = FALSE}
knitr::kable(rockets[,1:9],
             format = "html")
```

## Stats 2020

```{r}
stats_2020 <- get_SpaceX_launches(launch_year = 2020)

payload <- stats_2020$rocket$second_stage$payloads %>% 
  lapply(function(x){
  x %>%   
    select(payload_id, payload_type, payload_mass_kg)
  
}) %>% 
  bind_rows()
```

```{r}
payload
```





## Related projects
* [SpaceX](http://www.spacex.com/)
* [SpaceX-API](https://github.com/r-spacex/SpaceX-API)

