---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# SpaceX - An R API wrapper for the SpaceX project

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)


```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "##",
                      fig.retina = 2,
                      fig.align = "center",
                      fig.path = "README_figs/README-")
```

## Installation

Until now the package is not on CRAN but you can download it via GitHub with the following command:

```{r, eval = FALSE}
if (!require("devtools"))
  install.packages("devtools")
devtools::install_github("JohannesFriedrich/SpaceX")
```


## Introduction

The **R**-package *SpaceX* is an API wrapper for data collected by https://api.spacexdata.com/v3/ (version v3). You can request available data with different functions:

Function name       | Description                                        | Example
--------------------|----------------------------------------------------| -------
get_SpaceX_capsules()   | request information on capsules          | get_SpaceX_capsules("upcoming")
get_SpaceX_cores()      | request information on cores             | get_SpaceX_cores(core_serial = "B1037")
get_SpaceX_dragons()    | request information on dragon capsules   | get_SpaceX_dragons("dragon1")
get_SpaceX_history()    | request information on SpaceX history    | get_SpaceX_history()
get_SpaceX_info()       | request common information on SpaceX     | get_SpaceX_info()
get_SpaceX_landpads()   | request information on landpads          | get_SpaceX_landpads(id = "LZ-4")
get_SpaceX_launches()   | request information on launches          | get_SpaceX_launches(launch_year = 2020)
get_SpaceX_launchpads() | request information on launchpads        | get_SpaceX_launchpads(site_id = "ksc_lc_39a")
get_SpaceX_missions()   | request information on missions          | get_SpaceX_missions()
get_SpaceX_payloads()   | request information on payloads          | get_SpaceX_payloads()
get_SpaceX_rockets()    | request information on rockets           | get_SpaceX_rockets("falcon1")
get_SpaceX_ships()      | request information on ships             | get_SpaceX_ships()
get_SpaceX_roadster()    | request information on SpaceX roadster  | get_SpaceX_roadster()

## Request basic information from SpaceX API <a id="basic_information"></a>

First we load some needed packages. The function `get_SpaceX_info()` will deliver some information about the company.

```{r, warning=FALSE, message=FALSE}
library(SpaceX)
library(ggplot2)
library(dplyr)

info <- get_SpaceX_info()
```


```{r, eval = FALSE, echo = FALSE}
info
```

```{r echo=FALSE}
knitr::kable(
  info[,1:7],
  format = "html"
)
```

## Request upcoming starts

```{r upcoming launches}
upcoming <- get_SpaceX_launches("upcoming")
```

```{r, echo = FALSE}
knitr::kable(upcoming[1:3,1:9],
             format = "html")
```

## Play around with data

```{r past_launches}
get_SpaceX_launches() %>% 
ggplot() + 
  geom_bar(aes(launch_year, fill = launch_site$site_name)) +
  facet_grid(rocket$rocket_name~launch_success, scales = "free_x") +
  theme(legend.position = "bottom") + 
  scale_fill_discrete(name = "Launch Site") +
  labs(x = "Year", y = "Counts") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1))

```

Now we request some data about the used rockets. This can be done with the function `get_SpaceX_rockets()`.

```{r}
rockets <- get_SpaceX_rockets()
```

```{r, echo = FALSE}
knitr::kable(rockets[,1:9],
             format = "html")
```

## Stats 2020

```{r}
stats_2020 <- get_SpaceX_launches(launch_year = 2020)

```

```{r}
launchpads <- get_SpaceX_launchpads()
  
library(leaflet)
library(htmltools)

leaflet(launchpads) %>%
  addProviderTiles(providers$OpenStreetMap) %>% 
  addTiles() %>%  
  addMarkers(~location$long, ~location$lat, popup = ~htmltools::htmlEscape(location$name))
```

## Missions

```{r missions}
missions <- get_SpaceX_missions()
```


```{r, echo = FALSE}
knitr::kable(missions[,1:3],
             format = "html")
```

## SpaceX support ships

```{r ship}
ship <- get_SpaceX_ships(active = "true")
```

```{r, echo = FALSE}
knitr::kable(ship[1:4,1:7],
             format = "html")
```


## Related projects
* [SpaceX](http://www.spacex.com/)
* [SpaceX-API](https://github.com/r-spacex/SpaceX-API)

